%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
\name{Ho Young}{Jhoo}
\position{Graduate Student}
\address{D-503, 262 Achasan-ro, Gwangjin-gu, Seoul, South Korea}

\mobile{(+82) 10-9030-1843}
\email{mersshs@gmail.com}
%\dateofbirth{January 1st, 1970}
\homepage{sf.snu.ac.kr/hoyoung.jhoo}
\github{MerHS}
\linkedin{ho-young-jhoo-289710161}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Cruise LLC.}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Internship Application}
% How the letter is opened
\letteropening{Dear Cruise Recruiting team,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[L]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
{\today}
{Ho Young Jhoo~~~·~~~Cover Letter}
{}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

  % Beginning 
  I am excited that Cruise has opened an internship for distributed training. I agree that the lifecycle of massive data is essential for the practical implementation of the autonomous driving system. I would like an opportunity to handle and optimize real-world large-scale model with Cruise's advanced infrastructure.

  I am pursuing a Doctoral degree in Computer Science and Engineering at Seoul National University.
  My current interest is implementing an ML framework or compiler which is easy to use and, at the same time, ensures high throughput. With professor Nuno P. Lopes and Chung-Kil Hur, I have investigated distributed processing and parallelization frameworks for ML models such as Alpa and DeepSpeed. My current goal is to automatically find the optimal parallelization route of a given model with minimal user-defined settings.

  My work has focused so far in the analysis of computer vision models. I experienced and analyzed the whole process of constructing an ML model, including data pre-processing, training, and deployment. The implementation of each model uses PyTorch, TypeScript, and MLIR, which were the bleeding-edge technologies that didn't have much documentation at the time of the writing. My work would support understanding and optimizing the models from Cruise's self-driving platform.

  Additionally, I have full-time and internship working experience in several fields, from a startup company to the IT department of a national agency. Most recently, I participated in ML compiler optimization that reduces memory usage from the startup manufacturing DL accelerator. Also, I made a full-stack web app and mobile app based on Java and Scala from the Korean Air Force. I've also worked at a mobile game company, where I was in charge of the core part of the game system and collaborated with colleagues with diverse backgrounds. These experiences prove that I adapt to various companies and teams quickly and well.

  I believe my experiences and skills would be a great help for the opportunity. Thank you for your consideration, and I'm looking forward to joining the Cruise team.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
